Updated Criteria for the Diagnostic Procedure for Parkinson's Disease Dementia on Level I

### 2024-01-16 theart.qmd
methods section added to theart

---
title: "Level-1 PDD criteria something"
format: pdf
---

>>>>

---
title: "Updated Criteria for the Diagnostic Procedure for Parkinson's Disease Dementia on Level I"
shorttitle: "Parkinson's Disease Dementia Level I Criteria"
author:
  - name: Martina Kvapilova
    corresponding: false
    role:
      - Conceptualization
      - Data curation
      - Writing - original draft
    affiliations:
      - id: "1FM"
        name: "First Faculty of Medicine and General University Hospital in Prague, Charles University, Czech Republic"
        department: "Department of Neurology and Centre of Clinical Neuroscience"
  - name: Josef Mana
    corresponding: true
    orcid: "0000-0002-7817-3978" 
    email: "josef.mana@protonmail.com"
    role:
      - Conceptualization
      - Data curation
      - Investigation
      - Formal analysis
      - Software
      - Methodology
      - Project administration
      - Validation
      - Writing - original draft
    affiliations:
      - id: "1FM"
        name: "First Faculty of Medicine and General University Hospital in Prague, Charles University, Czech Republic"
        department: "Department of Neurology and Centre of Clinical Neuroscience"
  - name: Martin Cihak
    corresponding: false
    email: "martin.cih@gmail.com"
    role:
      - Conceptualization
      - Investigation
      - Methodology
      - Writing - original draft
    affiliations:
      - id: "1FM"
        name: "First Faculty of Medicine and General University Hospital in Prague, Charles University, Czech Republic"
        department: "Department of Neurology and Centre of Clinical Neuroscience"
  - name: Ondrej Bezdicek
    corresponding: false
    email: "ondrej.bezdicek@gmail.com"
    role:
      - Investigation
      - Data curation
      - Funding acquisition
      - Conceptualization
      - Project administration
      - Supervision
      - Writing - original draft
    affiliations:
      - id: "1FM"
        name: "First Faculty of Medicine and General University Hospital in Prague, Charles University, Czech Republic"
        department: "Department of Neurology and Centre of Clinical Neuroscience"
  - name: Tereza Uhrova
    corresponding: false
    email: "tereza.uhrova@vfn.cz"
    role:
      - Investigation
    affiliations:
      - id: "1FM"
        name: "First Faculty of Medicine and General University Hospital in Prague, Charles University, Czech Republic"
        department: "Department of Neurology and Centre of Clinical Neuroscience"
  - name: Robert Jech
    corresponding: false
    orcid: "0000-0002-9732-8947"
    email: "jech@cesnet.cz"
    role:
      - Funding acquisition
      - Resources
      - Writing - review & editing
    affiliations:
      - id: "1FM"
        name: "First Faculty of Medicine and General University Hospital in Prague, Charles University, Czech Republic"
        department: "Department of Neurology and Centre of Clinical Neuroscience"
abstract: ""
keywords:
  - Parkinson’s disease
  - dementia
  - level I criteria
format:
 apaquarto-pdf:
   documentmode: man
   a4paper: true
   pdf-engine: lualatex
   floatsintext: false
   keep-tex: false
bibliography: references.bib
---

{{< include _extensions/wjschne/apaquarto/_apa_title.qmd >}}

# Introduction

# Methods

## Participants

The data of patients with idiopathic PD diagnosed by a movement disorder specialist fulfilling the Movement Disorder Society (MDS) Clinical Diagnostic Criteria for Parkinson's disease (PD) [@postuma2015] were retrospectively gathered from clinical records acquired between January 2014 and December 2023. All the patients underwent a neuropsychological assessment by a trained clinical psychologist (OB) during a routine examination of cognitive functions as a part of the evaluation process for the indication of Deep Brain Stimulation (DBS) at General University Hospital in Prague. The Ethics Committee of the General University Hospital in Prague had approved the study protocol. All patients provided written informed consent prior to the examination.

## Neuropsychological Assessment

Participants were assessed with both MMSE (Stepankova et al., 2014; [@folstein1975] and MoCA [@kopecek2016]; [@nasreddine2005] to measure overall cognitive performance. Moreover, a comprehensive neuropsychological assessment was performed in accordance with MDS Task Force Level 2 criteria for MCI in PD [@litvan2012]. We described our battery including a regression based calculator for normative scores in another study [@bezdicek2017]. Besides other neuropsychological tests, the comprehensive assessment employed Clock Drawing Test (CDT) and Letter Fluency. To establish cognitive performance in individual cognitive domains according to Level 1 criteria for PDD, we used test scores proposed by Dubois et al., [@dubois2007] and their analogues in MoCA, see Table A for details.

Insert Table

To measure independence in activities of daily living, we administered Functional Activities Questionnaire (FAQ; Bezdicek et al., 201; [@pfeffer1982]. To assess neuropsychiatric functioning, we used Beck Depression Inventory II (BDI-II; [@ciharova2020]; [@beck1996] and State-Trait Anxiety Inventory (STAI; Spielberg et al., 1970, Mullner et al., 1980). Psychotic symptoms were assessed in an interview by a trained psychiatrist.

# Results

# Discussion

# References
